\documentclass{article}

% \usepackage[margin=1in]{geometry}

\title{\textsc{Machenical Usage of Binary Numeral System: Summary}}
\author{2021 Dongtan High School 30925 Han-Gyeol Jeon}

\begin{document}

\maketitle

\paragraph{Why I Selected to Presentate in This Subject}
I have heared many times that computer only works within 0's and 1's,
but I was yet curious of how the interpretation held.
For this, I thought I have to discouver how 0's and 1's work inside of the computer
in Binary Numeral side.

\paragraph{Binary Numeral System and Use in Computer System}
Binary Numeral System(\textit{binary} for now) is a numeral system which
constructed only within 0's and 1's.
What numeral system which we use in everyday life is constructed within
10 number characteristics, which is why the system called \textit{decimal}.
In binary, we can representate most of the things we can show with decimal.

Mathematicians was needed to know how to representate data within
\textit{numbers}, not \textit{binary}.
In this stream, mathematicians from all around the world declared
data structures that can used to show data inside of the computer,
and some of those was chosen by Operating System developers in huge companies
and programmers.
In this presentation, I handled about representation of integers, rational numbers,
literal strings, and videos.

To attach this data into our everyday life, it is needed of calculation process that
sends variables in everyday life into program, and responsibility of these
calculations are in softwares that constructed with logical negation and summation.
Those who are called \textit{programmers} develops these softwares.

\paragraph{Thoughts}
After studying computer science,
I had be able to compare between digital data handling
held in computer and those of in everyday life. For this, I was affected in
world indicating side, changing my basis philosophy in living life afterward.

There could be many frictions by technological development:
The misusage of technology that can be after development of brainwave processing
| like control of human behaviour by doing it to real human brain, resulting great
recognition problem | is those of that.
For getting off of these problems, we need to have politically correct
recognition philosophy, and also effort for politically correct education by
doable educators.

\end{document}